Growth of _E. coli_ in mSSB lab 

### 2022-10-17 mssb_2.2_2022.Rmd
debugging github display

```{r organize plate readings, echo=TRUE, message=FALSE}
# Reorganize the platemap
platemap_tidy = platemap %>%
  pivot_longer(cols=2:13, names_to="wellcol", values_to="Treatment") %>%
  unite("Well", Colonne1, wellcol, sep="")

@@

```{r plot plate readings, echo=TRUE, message=FALSE}

@@

```{r growth curve comparison, echo=TRUE}
# Do pairwise comparisons between groups of growth curves at OD600 using a permutation test.
# 1 is plasmid 87
# 2 is plasmid 261
# 3 is water
# 4 is plasmid 75

@@

```{r growth curve fluorescent protein, echo=TRUE}
# To explore the toxicity of producing a fluorescent protein will test growth of plasmid #2 
# (261) as a control of carrying the burden of a plasmid against the burden of carrying a 
# fluorescent plasmid in #1 (87) and #4 (75).

@@

Finally we explore the limits of detection given our experimental setup. We plot the detection of plasmid 261 without any integrase in the "mKate" channel (fluorescence intensity at 590 nm). We also plot the untransformed WT _E. coli_. We see the readings are non-zero in the channel, even when reading samples that should not be emitting fluorescence. 
```{r limits of detection, echo=TRUE}
# To explore the limits of detection we will test fluorescence of plasmid #2 
# (261) detected at 590nm (two plots for two excitation wavelengths).

>>>>

```{r organize_plate_readings, echo=TRUE, message=FALSE}
# Reorganize the platemap
platemap_tidy = platemap %>%
  pivot_longer(cols=2:13, names_to="wellcol", values_to="Treatment") %>%
  unite("Well", Colonne1, wellcol, sep="")

@@

```{r plot_plate_readings, echo=TRUE, message=FALSE}

@@

```{r growth_curve_comparison, echo=TRUE}
# Do pairwise comparisons between groups of growth curves at OD600 using a permutation test.
# 1 is plasmid 87
# 2 is plasmid 261
# 3 is water
# 4 is plasmid 75

@@

```{r growth_curve_fluorescent_protein, echo=TRUE}
# To explore the toxicity of producing a fluorescent protein will test growth of plasmid #2 
# (261) as a control of carrying the burden of a plasmid against the burden of carrying a 
# fluorescent plasmid in #1 (87) and #4 (75).

@@

Finally we explore the limits of detection given our experimental setup. We plot the detection of plasmid 261 without any integrase in the "mKate" channel (fluorescence intensity at 590 nm). We also plot the untransformed WT _E. coli_. We see the readings are non-zero in the channel, even when reading samples that should not be emitting fluorescence.

```{r limits_of_detection, echo=TRUE}
# To explore the limits of detection we will test fluorescence of plasmid #2 
# (261) detected at 590nm (two plots for two excitation wavelengths).
